The Way Forward in Parallelizing Dynamic Languages

### 2014-05-02 talk/icooolps2014/position-paper.tex
additions

The first obvious candidate to replace the GIL is to use multiple
locks instead of a single global lock. By refining the granularity of
the locking approach, we gain the ability to run code that does not
access the same objects in parallel. What we lose instead is the
simplicity of the GIL approach. With every additional lock, the
likeliness of deadlocks grows, as well as the overhead that acquiring
and releasing locks produces.

@@

\subsubsection{Shared-Nothing / multiple processes}

>>>>

The first obvious candidate to replace the GIL is to use multiple
locks instead of a single global lock. By refining the granularity of
the locking approach, we gain the ability to run code that does not
access the same objects in parallel. What we lose instead is the
simplicity of the GIL approach. With every additional lock, the
likeliness of deadlocks grows, as well as the overhead that acquiring
and releasing locks produces. The former means that sometimes it is
necessary to fall back to less fine-grained locking, preventing some
potential parallelism in order to keep the complexity manageable.
The latter means that we lose a bit of performance in the
single-threaded case compared to the GIL, which requires much less
acquire-release operations.

@@

\subsubsection{Shared-Nothing}
